\input{./head/preamble.tex}

\addtolength{\oddsidemargin}{1in}
\addtolength{\evensidemargin}{1in}
\addtolength{\textwidth}{-2in}
\linespread{1.5}

\begin{document}

\input{./head/header.tex}
\vspace{3em}

\noindent \texttt{
<BEGIN TRANSMISSION>
SUBJECT: WORK ASSIGNMENT
}
\hfill
{\bf\today}
\vspace{1em}

I'm applying for the positions of Tools Programmer, UI Developer, or Render
Programmer with specific interest in helping polish and refine Elite:
Dangerous. I've played nearly all of the titles but E:D remains specifically
near and dear to my heart. No other game lets you traverse the galaxy in such a
realistic simulation. That said, I'm also excited about the overlap in both the
engine and features of the other games like Planet Zoo and Planet Coaster (PC
G-force simulations are interesting, for example).

In my previous roles as a developer at Apple, America's Test Kitchen, and
Forward Financing, I have created and deployed both backends and frontends to
customers who depend on the ability to quickly and easily use the software. I
know the difference small things can make to the user's experience and work
hard so that everything lives up to a high standard of quality. For a game
especially like Elite, which takes place in the vacuum of space, clunky,
bloated functions simply will not do. I aspire to create clean, simple, minimal
interfaces and abstractions so that players and developers can almost forget
they are there and focus on the stars. I would be thrilled to join the team(s)
continuing to make this vision a reality for the millions of players here on
Earth.

Between my previous job experience on many full-stack projects and a intensive
study of GPU architecture during my time at Northeastern University, I have
accumulated a breadth of knowledge that is applicable to anything from UI/UX
design to low level systems or graphics programming. I have experience
maintaining a GPU accelerated terminal emulator, as well as many of my own toy
projects. My passion for compilers and programming languages leads me towards
deeper understandings of the tools I use, which is generally a requirement of
developing fast and correct programs.

This job would help me reach my goals as a software engineer by exposing me to
more graphics engineering and other performance critical systems. I'm always
looking to improve both the quality of my own code as well as my ability to
debug and benchmark the software I'm dealing with. Working for a company with
their own engine and simulation games would be a great fit since performance
really matters here, as does the user's experience. Whether I'd be working on
the engine itself, or using the frameworks provided to give users accessible
and responsive controls, I feel confident that my abilities as a designer,
architect, and programmer will be put to good use.

\vspace{1.5em}
\noindent Thank you for your consideration.\\
\noindent \texttt{O7, CMDR nixpulvis signing off.}

\end{document}
